A Large-Scale Study of the Use of Eval in R

### 2020-08-22 inst/paper/main.tex
intro

\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\eval}{\c{eval}}

\begin{abstract}
  The \c{eval} function turns text into code. The widespread use of that
  capability hinders the static reasoning about software systems. This paper
  is a large-scale study of a corpus of \miss{3} million lines of R code.
  We performed static and dynamic analysis of our corpus and report that
  usage of \c{eval} is indeed wide spread. It is used by expert core
  developers of the language, experienced library developers, and end-users
  alike. The patterns of usage range from meta-programming to
  misunderstandings of what \c{eval} is good for. Case studies give example
  use-cases and some evidence that automated tools could be used to refactor
  some of the uses of \c{eval}.
\end{abstract}

>>>>

\newcommand{\eval}{\texttt{eval}\xspace}

\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}

\begin{abstract}
  The \eval function turns text into code. From the point of view of
  reasoning about software system, uses of \eval turn the program's code
  from a statically known quantity that can be reasoned about and analyzed
  into one of the inputs to the program. Thus, widespread use of \eval
  hinders our ability to provide safety and security guarantees for
  software. Understanding how \eval is used in practice is key to finding
  ways to mitigate its damage. One question that has not been studied is
  whether the usage of \eval is dependent on the application domain or other
  features of the language. This paper is a large-scale study of a corpus of
  \miss{3} million lines of data science libraries and end-user written in
  the R language. We performed a simple static analysis and more
  sophisticated dynamic analysis to confirm that \eval is indeed in wide
  spread use, and to categorized patters of usage. We found that \eval in
  this code base is more dangerous in some ways, and safer in others, than
  what was previously reported for JavaScript.
\end{abstract}
